### 2013-06-10 Rcode/intro.rmd
added comparison of localfdr from auto and non-auto methods

>>>>

[for testing: note that the PosteriorMean and PositiveProb don't depend much on sigmaa vec used ]
```{r}
plot(beta.ash.auto$PosteriorMean, beta.ash$PosteriorMean, xlab="Shrunk estimate from auto method", ylab="Shrunk estimate from fixed method")
abline(a=0,b=1)
plot(beta.ash.auto$localfdr, beta.ash$localfdr, xlab="lfdr from auto method", ylab="ldfr from fixed method")
abline(a=0,b=1)
```
